%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Teaching}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Year 1 Project Supervisor} % Affiliation/role
    {Faculty of Natural Sciences} % Organization/group
    {Imperial College London} % Location
    {Jan. 2017 --- May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Was in charge of two first year students who worked as a pair.}
        \item {Their project was concerned with the identification of active regions (spots and faculae) on the solar surface.}
        \item {Images from HMI/SDO were analysed using Python image processing tools.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Laboratory Practicum Assistant} % Affiliation/role
    {Department of Mechanical Engineering} % Organization/group
    {ETH Z{\"u}rich} % Location
    {Sep. 2013 --- Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Conducted the laboratory experiment practice instruction for about 25 students each semester.}
        \item {Marked the lab experiment reports.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Physics III Course Assistant} % Affiliation/role
    {Department of Physics} % Organization/group
    {ETH Z{\"u}rich} % Location
    {Sep. 2012 --- Feb. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Conducted excercise classes on optics, statistical mechanics and quantum mechanics for a group of about 20 students.}
        \item {Marked the excercise sheets.} 
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Physics II Course Assistant} % Affiliation/role
    {Department of Physics} % Organization/group
    {ETH Z{\"u}rich} % Location
    {Jan. 2012 --- May 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Conducted excercise classes on classical mechanics for a group of about 20 students.}
        \item {Marked the excercise sheets.} 
        \item {Shared the role with one more assitant.}
      \end{cvitems}
    }

\end{cventries}
